Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-11 draft/accordionComplexSurfaces.tex
fan and polytope

We have borrowed \fref{fig:fanAssociahedron} from~\cite{PaluPilaudPlamondon} to illustrate Theorem~\ref{thm:fanAssociahedron}.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.5]{fanAssociahedron1}}
	\centerline{\includegraphics[scale=.5]{fanAssociahedron2}}
	\caption{The $\b{g}$-vector fan~$\gvectorFan$ (left) and the $\bar Q$-associahedron~$\Asso$ (right) of two gentle quivers. Illustration borrowed from~\cite{PaluPilaudPlamondon}.}
	\label{fig:fanAssociahedron}
\end{figure}

>>>>

\fref{fig:fanAssociahedron} illustrates Theorem~\ref{thm:fanAssociahedron}.

\begin{figure}[p]
	\capstart
	\centerline{\includegraphics[scale=.5]{fanAssociahedron1}}
	\vspace{.5cm}
	\centerline{\includegraphics[scale=.5]{fanAssociahedron2}}
	\vspace{.5cm}
	\centerline{\includegraphics[scale=.5]{fanAssociahedron3}}
	\caption{The $\b{g}$-vector fan~$\gvectorFan$ (left) and the $\bar Q$-associahedron~$\Asso$ (right) of three locally gentle quivers. The first two are gentle and the illustration is borrowed from~\cite{PaluPilaudPlamondon}. The last is locally gentle but not gentle.}
	\label{fig:fanAssociahedron}
\end{figure}
